Robust Adaptation to Multi-Scale Climate Variability

### 2019-01-08 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
fix language in discussion of new figure

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
As shown in \cref{fig:m-n-sketch}, the importance of predicting, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
When $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and increases in model complexity only add uncertainty.
If $M$ is short and $N$ is long, however, the \gls{lfv} in the system may be skillfully predicted, thereby reducing the cost of such an instrument.
If $N$ remains long but $M$ increases, then informational uncertainty may be reduced, but intrinsic uncertainty will remain, and may be large.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{M-N-Sketch.pdf}
  \caption{
    The importance of predicting different signals, and the identifiability and predictability of the signals, depends on the degree of informational uncertainty ($N$) and the project planning period ($M$).
  }\label{fig:m-n-sketch}
\end{figure}
We also showed that the importance of predicting, and potential for doing so skillfully, depend on the project planning period $M$ and the information available, $N$.
\Cref{fig:m-n-sketch} shows that when $M$ and $N$ are short, only a ``rough guess'' using simple models is feasible, and more complex models  only add uncertainty.
As $N$ increases, however, the potential for skillful prediction of \gls{lfv} over the short planning period increases, thereby reducing the cost of a flexible or adaptive instrument.
If $M$ is large, \ie a permanent plan is considered, then informational uncertainty may be addressed with sufficient information (large $N$), but large intrinsic uncertainty may remain.
Finally, if $M$ is long but $N$ is short, then the analysis will lead to the ``danger zone'' of extrapolation and a high potential for misleading estimates.
